Near infrared spectrum of a Class 0 protostar photosphere

### 2017-05-08 document/ms.tex
Update the ms and post the most recent pdf version of the ms.

The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and assumed irretrievable---way.  So instead of characterizing the spectral slope by a reddening law and extinction, $A_V$, we instead assume that the overall spectral shape is approximated by a third order polynomial \footnote{The polynomial is parameterized as a linear combination of Chebyshev polynomials truncated to the first 3 non-constant terms.}.

We assume there is zero emission attributable to mass accretion onto the star or disk.  This assumption almost certainly fails for Class 0 protostars, which are still actively accreting a large fraction of their mass.  However, the dearth of any conspicuous emission lines suggests that perhaps the S68N is going through a quiescent phase in a variable accretion history.  In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[\emph{e.g.}]{2016ApJ...826..179L}.

@@

\tabcolsep=0.11cm
%\rotate
\tablecaption{Exeriment log \label{tbl_history}}
\tablewidth{0pt}
\tablehead{
\colhead{Exp.} &
\colhead{Run.} &
\colhead{Desc.} &
\colhead{Outcome}
\\
\colhead{\#} &
\colhead{\#} &
\colhead{-} &
\colhead{-}
}
\startdata
 1 & 1 & Original, flawed \texttt{star\_veil.py} code modeled disk radiance as a constant value with no physical interpretation & Exposed need for more physical inputs \\
2 & 1 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, weak priors, poor first guess & Exposed need for better priors and starting guess \\
2 & 2 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, strong priors ($T_{d}$ fixed to $\sim1100$ K), good first guess & Exposed incorrect $\Omega$ treatment \\
3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
3 & 2 & \emph{In progress:} Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide range \\
\enddata
\end{deluxetable*}

>>>>

The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and potentially irretrievable---way.  We explored several options for characterizing the extinction towards S68N.  First, instead of characterizing the spectral slope by a reddening law and extinction, $A_V$, we instead assumed that the overall spectral shape is approximated by a third order polynomial \footnote{The polynomial is parameterized as a linear combination of Chebyshev polynomials truncated to the first 3 non-constant terms.}.  The polynomial coefficients lacked interpretability, and may not have adequately approximated extinction power laws, so we also experimented with an $A_K$ and a power law slope:

$$ A_\lambda / A_K = \frac{\lambda}{2.2 \; \mu\mathrm{m}}^\alpha$$

with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.

We assume there is zero emission attributable to mass accretion onto the star or disk.  This assumption almost certainly fails for Class 0 protostars, which are still actively accreting a large fraction of their mass.  We see H$_2$ emission lines in the $K-$band spectrum of S68N, so some degree of accretion is likely ongoing, potentially contributing non-negligible veiling in the photospheric absorption lines.  In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[\emph{e.g.}]{2016ApJ...826..179L}.

@@

\tabcolsep=0.11cm
%\rotate
\tablecaption{Exeriment log \label{tbl_history}}
\tablewidth{0pt}
\tablehead{
\colhead{Exp.} &
\colhead{Run.} &
\colhead{Desc.} &
\colhead{Outcome}
\\
\colhead{\#} &
\colhead{\#} &
\colhead{-} &
\colhead{-}
}
\startdata
 1 & 1 & Original, flawed \texttt{star\_veil.py} code modeled disk radiance as a constant value with no physical interpretation & Exposed need for more physical inputs \\
2 & 1 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, weak priors, poor first guess & Exposed need for better priors and starting guess \\
2 & 2 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, strong priors ($T_{d}$ fixed to $\sim1100$ K), good first guess & Exposed incorrect $\Omega$ treatment \\
3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
3 & 2 & Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide posteriors \\
5 & 1 &  Windowing on CO and Na~I, $T_{d}$ fixed to $\sim1100$ K & Slightly higher $T_{\mathrm{eff}}$ and $\log{g}$ compared to just CO window.\\
6 & 1 &  Introduce $A_V$, with fixed ($\alpha=-2.0$) slope, $\log{g}>2.0$, Chebyshev $6\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors than before\\
7 & 1 &  $A_V$, with variable ($\alpha \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors due to tighter Chebyshev, $\alpha$ limit exceeded\\
8 & 1 &  $A_K$, with variable ($\alpha \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Re-running\\
\enddata
\end{deluxetable*}
